Double White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-07-29 papers/wdmerger_I/paper.tex
Add references and acknowledgements for a few more community resources.

The software used to generate the test problems in this paper
(as well as the manuscript itself),
\texttt{wdmerger}\footnote{\url{https://github.com/BoxLib-Codes/wdmerger}},
is freely available at an online repository hosting service.
Version control in both the parent software (BoxLib, CASTRO) and in \texttt{wdmerger}
permits us to reference the state of the code at the time a simulation
was performed. In all plot files and diagnostic output generated by CASTRO, 
and EPS figure files and plots generated by \texttt{wdmerger} for this work,
we store the active \texttt{git} commit hashes of BoxLib, CASTRO and \texttt{wdmerger}.

@@

@@

We comment on the choice of reference state for passively-advected
quantities (like $X_k$ or the transverse velocity), which is not typically 
discussed. First, consider one of the variables present in one-dimensional flow
(density, velocity in the normal direction, and pressure), and let our 
reference state be as in Eq.~\autoref{eq:refchoice}.
Ignoring flattening, if there are no waves moving toward our
interface, then Eq.~\autoref{eq:ppmstatel} reduces to:
\begin{equation}
q_{i+1/2,L}^{n+1/2} = \tilde{q}_L = q_i
\end{equation}
If instead only the fastest wave is moving toward the interface, then
only the term corresponding to the fastest wave in the sum will be
added in Eq.~\autoref{eq:ppmstatel}, but our choice of reference state makes
that term zero by design, and our interface state is:
\begin{equation}
q_{i+1/2,L}^{n+1/2} = \tilde{q}_L = \mathcal{I}_+^{+}(q_i)
\end{equation}
This is the desired behavior for each of these cases.

However, now consider the same approach applied to passively advected quantities.
If we use the same idea of the reference state as
in Eq.~\autoref{eq:refchoice}, and consider a quantity $\xi$ which should only
jump across the contact, then our interface state becomes:
\begin{equation}
\xi_{i+1/2,L}^{n+1/2} = \tilde{\xi}_L -
  \underbrace{l_i^\evz \cdot \left [
        \tilde{\xi}_L  - \mathcal{I}^\evz_+(\xi_i)
       \right ] r_i^\evz}_{\text{only if~$u \ge 0$}}
\end{equation}
Again, ignoring flattening, if $u \ge 0$, then we have
\begin{equation}
\xi_{i+1/2,L}^{n+1/2} = \tilde{\xi}_L -
  \left (\tilde{\xi}_L  - \mathcal{I}^\evz_+(\xi_i) \right ) = \mathcal{I}^\evz_+(\xi_i)
\end{equation}
(where we used the fact that the eigenvectors are normalized to unity and
don't mix in any other states when dealing with passive terms).  This
is the expected behavior---we see a state that is traced only by the
contact wave.  However, if $u < 0$ but $u + c \ge 0$, then we instead get:
\begin{equation}
\xi_{i+1/2,L}^{n+1/2} = \tilde{\xi}_L = \mathcal{I}^\evp_+(\xi_i)
\end{equation}
Here we used the same definition of the reference state and see that our
interface state sees the profile traced under the fastest wave, not the
contact.  This is not the correct behavior for a passively-advected
quantity.

>>>>

The software used to generate the test problems in this paper
(as well as the manuscript itself),
\texttt{wdmerger}\footnote{\url{https://github.com/BoxLib-Codes/wdmerger}},
is freely available at an online repository hosting service.
Version control in both the parent software (BoxLib, CASTRO) and in \texttt{wdmerger}
permits us to reference the state of the code at the time a simulation
was performed. In all plot files and diagnostic output generated by CASTRO, 
and EPS figure files and plots generated by \texttt{wdmerger} for this work,
we store the active \texttt{git} commit hashes of BoxLib, CASTRO and \texttt{wdmerger}.
Line plots are generated using the \texttt{matplotlib} library for \texttt{Python} 
\cite{matplotlib}, while slice plots and other multi-dimensional visualizations are 
generated using the \cite{yt} code.

@@

This research has made use of the AstroBetter blog and wiki. 
This research has made use of NASA's Astrophysics Data System 
Bibliographic Services.

@@

We comment on the choice of reference state for passively-advected
quantities (like $X_k$ or the transverse velocity), which is not typically 
discussed. First, consider one of the variables present in one-dimensional flow
(density, velocity in the normal direction, and pressure), and let our 
reference state be as in \autoref{eq:refchoice}.
Ignoring flattening, if there are no waves moving toward our
interface, then \autoref{eq:ppmstatel} reduces to:
\begin{equation}
q_{i+1/2,L}^{n+1/2} = \tilde{q}_L = q_i
\end{equation}
If instead only the fastest wave is moving toward the interface, then
only the term corresponding to the fastest wave in the sum will be
added in \autoref{eq:ppmstatel}, but our choice of reference state makes
that term zero by design, and our interface state is:
\begin{equation}
q_{i+1/2,L}^{n+1/2} = \tilde{q}_L = \mathcal{I}_+^{+}(q_i)
\end{equation}
This is the desired behavior for each of these cases.

However, now consider the same approach applied to passively advected quantities.
If we use the same idea of the reference state as
in \autoref{eq:refchoice}, and consider a quantity $\xi$ which should only
jump across the contact, then our interface state becomes:
\begin{equation}
\xi_{i+1/2,L}^{n+1/2} = \tilde{\xi}_L -
  \underbrace{l_i^\evz \cdot \left [
        \tilde{\xi}_L  - \mathcal{I}^\evz_+(\xi_i)
       \right ] r_i^\evz}_{\text{only if~$u \ge 0$}}
\end{equation}
Again, ignoring flattening, if $u \ge 0$, then we have
\begin{equation}
\xi_{i+1/2,L}^{n+1/2} = \tilde{\xi}_L -
  \left (\tilde{\xi}_L  - \mathcal{I}^\evz_+(\xi_i) \right ) = \mathcal{I}^\evz_+(\xi_i)
\end{equation}
(where we used the fact that the eigenvectors are normalized to unity and
don't mix in any other states when dealing with passive terms).  This
is the expected behavior---we see a state that is traced only by the
contact wave.  However, if $u < 0$ but $u + c \ge 0$, then we instead get:
\begin{equation}
\xi_{i+1/2,L}^{n+1/2} = \tilde{\xi}_L = \mathcal{I}^\evp_+(\xi_i)
\end{equation}
Here we used the same definition of the reference state and see that our
interface state sees the profile traced under the fastest wave, not the
contact.  This is not the correct behavior for a passively-advected
quantity.
